Title Goes Here

### 2019-04-23 analysis/paper/paper.Rmd
fixed paper, added dockerfile for testing

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

header-includes:
  - \raggedbottom

documentclass     : "apa6"
classoption       : "jou, a4paper, noextraspace"
output            : papaja::apa6_pdf
nocite: |

@@

```{r setup, include = FALSE}
library("papaja")
library(here)
load(here::here("analysis", "data", "completed_analysis.rda"))
# source(here("Analysis Programs", "Figures", "manuscript_figs.r"))
# use this to allow custom decimal places later on
op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

```{r methodFig, fig.align='center', fig.cap = '(ref:methodFig)', out.width='100%'}
knitr::include_graphics(here("analysis", "figures", "Methods_fig.png"), dpi = 300)

@@

```{r OmissionPlot, fig.align='center', fig.cap = '(ref:omissions)', out.width='100%'}
knitr::include_graphics(here("analysis", "figures", "omission_plot.png"), dpi = 300)

@@

```{r SaccadePlot, fig.align='center', fig.cap = '(ref:saccadeFig)', out.width='100%'}
knitr::include_graphics(here("analysis", "figures", "saccade_plot.png"), dpi = 300)

@@

```{r blockPlot, fig.align='center', fig.cap = '(ref:blockFig)', out.width='100%'}
knitr::include_graphics(here("analysis", "figures", "capture_plot_by_block.png"), dpi = 300)

@@

```{r VincentizedPlot, fig.align='center', fig.cap = '(ref:vincentizedFig)', out.width='100%'}
knitr::include_graphics(here("analysis", "figures", "vincentized_plot.png"), dpi = 300)

@@

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
csl               : "american-psychological-association-6th-edition_no_first_citation.csl"
header-includes:
  - \raggedbottom

documentclass     : "apa6"
classoption       : "man, a4paper, noextraspace, 11pt"
output            : papaja::apa6_pdf
nocite: |

@@

```{r setup, include = FALSE}
library("papaja")
library(here)

# Source analysis_report.R (the R code from analysis_report.Rmd) to allow this document to have access to  all analyses necessary for manuscript.
source(here::here("analysis", "analysis_report.R"))

# use this to allow custom decimal places later on
op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
```

```{r analysis-preferences, echo=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

@@

```{r methodFig, echo=FALSE, fig.align='center', fig.cap='(ref:methodFig)', fig.pos="!h", out.width='80%'}
knitr::include_graphics(here("analysis", "figures", "Methods_fig.png"), dpi = 300)

@@

```{r OmissionPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:omissions)', out.width='60%', fig.pos = "!h"}
knitr::include_graphics(here("analysis", "figures", "omission_plot.png"), dpi = 300)

@@

```{r SaccadePlot, echo=FALSE, fig.align='center', fig.cap = '(ref:saccadeFig)', out.width='80%', fig.pos = "!h"}
knitr::include_graphics(here("analysis", "figures", "saccade_plot.png"), dpi = 300)

@@

```{r blockPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:blockFig)', out.width='60%', fig.pos = "!h"}
knitr::include_graphics(here("analysis", "figures", "capture_plot_by_block.png"), dpi = 300)

@@

```{r VincentizedPlot, echo=FALSE, fig.align='center', fig.cap = '(ref:vincentizedFig)', out.width='60%',fig.pos = "!h"}
knitr::include_graphics(here("analysis", "figures", "vincentized_plot.png"), dpi = 300)

@@

# References
```{r create_r-references, echo=FALSE}
r_refs(file = "r-references.bib")
```
